---
title: "Aquatic Plant Community Restoration"
author: "Kate Sinnott"
date: "4/27/2021"
output: html_document
---

# Improving Establishment in Aquatic Plant Restoration Through Planting Method

Paragraph about SAV restoration

I want to know if the belowground biomass differs between planting methods. Stuckenia pectinata forms root tubers, which are a crucial part of how they survive the winter, disperse, and grow back rapidly following disturbance. Their rhizomes contribute to sediment stabilization, a ecosystem function in the highly turbid Utah Lake ecosystem. aMeasuring belowground biomass is a proxy for tuber and rhizome development. 

I want to make a bar plot showing below-ground biomass across treatments. First, I need to install tidyverse: 

```{r ggplot, eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse) 
```

Then I can combine the "Functional traits" and "Plot tables", build the bar plot, and save it as an image in ggplot.

```{r data viz 1, echo = TRUE, eval = FALSE}
functional_traits %>% 
  left_join(plots, by = "plot_id") %>% 
  mutate(p_m = case_when(
    planting_method == "hand_clump" ~ "Hand-planted (clumped)",
    planting_method == "hand_space" ~ "Hand-planted (spaced)" ,
    planting_method == "wrap_clump" ~ "Burlap wrap (clumped)",
    planting_method == "wrap_space" ~ "Burlap wrap (spaced)"
  )) %>% 
  ggplot(mapping = aes(x= p_m, 
                       y = below_biomass_g, 
                       fill = p_m)) +
  geom_col() +
  labs(x = "Planting method", y = "Belowground biomass (g)") +
  theme_light() + 
  theme(legend.position = "none") +
  ggsave(filename = "barplot.tiff",
         device = "tiff")
```


```{r barplot figure, echo=FALSE, eval=TRUE, fig.cap="Belowground biomass by planting method", fig.align='center', out.width='100%'}
knitr::include_graphics("/Users/katesinnott/Desktop/WILD_6900/SAV_restoration/SAV_restoration_book/barplot.tiff")
```