---
title: "Aquatic Plant Community Restoration"
author: "Kate Sinnott"
date: "4/27/2021"
output: html_document
---

# Improving Establishment in Aquatic Plant Restoration Through Planting Method

Paragraph about SAV restoration

I want to know if the belowground biomass differs between planting methods. Stuckenia pectinata forms root tubers, which are a crucial part of how they survive the winter, disperse, and grow back rapidly following disturbance. Their rhizomes contribute to sediment stabilization, a ecosystem function in the highly turbid Utah Lake ecosystem. aMeasuring belowground biomass is a proxy for tuber and rhizome development. 

I want to make a bar plot showing below-ground biomass across treatments. First, I need to install tidyverse: 

```{r ggplot, eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse) 
```

Then I can combine the "Functional traits" and "Plot tables", build the bar plot, and save it as an image in ggplot.

```{r data viz 1, echo = TRUE, eval = FALSE}
functional_traits %>% 
  left_join(plots, by = "plot_id") %>% 
  ggplot(mapping = aes(x= planting_method, 
                       y = below_biomass_g, 
                       fill = planting_method)) +
  geom_col() +
  labs(x = "Planting method", y = "Belowground biomass (g)") +
  theme_light() + 
  theme(legend.position = "none") +
  ggsave(filename = "barplot.tiff",
         device = "tiff")
```